Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-10-06 manuscript/manuscript.tex
Modofications to implementation in manuscript

We have developed a Python library that computes the gravity fields generated by any Tesseroid with variable density in depth through the GLQ to numerically approximate the volume integrals.
It's freely available under the BSD 3-clause open-source library and can be downloaded from the following repository: \todo{agregar repo, vale la pena poner el link?}

Although it's a Python library, the core functions of the computation are written in Cython, a superset of Python language that allows to generate efficient C code through the Cython compiler.
This produces a precompiled library whose functions can be called from regular Python code, what allowed us to make it compatible with the preexisting open-source library Fatiando a Terra \citep{Uieda2013}.

Its usage is very similar to the code for homogeneous tesseroid already in Fatiando a Terra (version 0.5):

\begin{enumerate}
\renewcommand{\theenumi}{(\arabic{enumi})}
    \item Define a single tesseroid (or a tesseroid mesh) with the Fatiando a Terra classes.
    \item Add a predefined Python density function to the tesseroid (or each tesseroid in the mesh).
    \item Calculate the desired gravity field (potential, gradient or tensor component) in any set of computation points with our new functions.
\end{enumerate}

The existing code in Fatiando a Terra (v.~0.5) for homogeneous tesseroid is optimised through the Numba compiler.
Due to difficulties when passing a Python function as argument of precompiled Numba methods, we have decided to rewrite them in Cython language, keeping the homogeneous tesseroid calculation and adding the new variable density code.

>>>>

We have developed a Python library that computes the gravity fields generated by any Tesseroid with variable density in depth.
It is freely available under the BSD 3-clause open-source library and can be downloaded from the following repository: \todo{agregar repo, vale la pena poner el link?}

This new library is based on the preexisting code developed by \citet{Uieda2016} (and included in Fatiando a Terra v.0.5, \citet{Uieda2013}) that is able to compute only the gravitational effects of tesseroids with homogeneous density.
\citet{Uieda2016} have optimised the more time consuming functions through the Numba compiler.
In contrast, we have decided to develop our new library in Cython language due to difficulties when passing a Python function as argument to precompiled Numba methods, keeping the homogeneous tesseroid calculation and adding the new variable density computations.
The Cython language is a superset of Python language that allows to generate efficient C code through the Cython compiler, producing a library whose functions can be called from regular Python code.

Moreover, this new software is compatible with the preexisting open-source library Fatiando a Terra and its usage is very similar to the one for homogeneous tesseroids:

\begin{enumerate}
\renewcommand{\theenumi}{(\arabic{enumi})}
    \item Define a single tesseroid (or a set of several tesseroids) with the Fatiando a Terra classes.
    \item Add a predefined Python density function to the tesseroid (or to each tesseroid in the set).
    \item Calculate the desired gravity field (potential, gradient or tensor components) on any set of computation points.
\end{enumerate}

In a more detailed way, the new library approximates the gravitational effect of each tessseroid through the GLQ, and increases its accuracy with the modified version of the adaptive discretization algorithm, original developed by \citet{Li2011} and improved by \citet{Uieda2016}.

Due to a new type of approximation error resulting from high variations in the density functions we had to develop a new density-based discretization algorithm that also intent to increase the accuracy, working together with the preexisting adaptive discretization algorithm.
